### 2016-01-18 paper.tex
Move strut drag section after performance; resolves #39
Note how similar C_D for high drag struts helps support the Re-independence of C_D at lower Re

@@

Strut drag losses do not change much for the streamlined NACA 0021 struts in the
towed versus stationary configuration. However, for the cylindrical struts,
losses increase significantly when towed and operating in the mid range of tip
speed ratios. With respect to numerical modeling, these measurements will allow
support struts to be simulated without blades, to isolate and evaluate the
ability to predict these losses independent of the blade loading.

>>>>

Strut drag losses do not change much for the streamlined NACA 0021 struts in the
towed versus stationary configuration, which helps explain why overall rotor
drag coefficients remain relatively constant even at low Reynolds number, were
$C_P$ is dramatically reduced, or even negative. For the cylindrical struts,
losses increase significantly when towed and operating in the mid range of tip
speed ratios. Though a real turbine would never use such high drag struts, with
respect to numerical modeling, these measurements will allow support struts to
be simulated without blades, to isolate and evaluate the ability to predict
these losses independent of the blade loading.

@@
